---
title: "Festivus Games"
execute:
  echo: false
---

```{r setup}
#| include: false
library(knitr)
```

## The Grand Festivus Games

```{r}
data.frame(label = c('Players', 'Level', 'Time'),
           comment = c('3 - 5', '3', '2 - 3 hours')) |>
  kable(col.names = rep('', 2))
```

### Background

You all have come to Sondheim for the Grand Festivus Games. The games occur every 10 years, and the town is alive with excitement in anticipation of the games, with visitors of all races from all over the continent.

Each individual’s motives for attending are different, but most are in it for either money or power: merchants selling wares, both common and rare; wealthy individuals and politicians, some who want to be seen, others who want to influence from the shadows; rogues and scoundrels who will con you out of your socks if you aren’t careful; assassins with contracts to carry out.

And then there are 30 men and women who are either brave or foolish, depending on who you ask. They are at the center of the Grand Festivus Games. They are the contestants who will risk life and limb for great reward.

You are contestants, and you plan to take away the grand prize. (You’ve heard that the person who won ten years ago now commands her own militia for hire and is living off the fat of her winnings on a private island in the Sea of Tears.) Only one contestant will win, and according to the official rules, contestants are not allowed to make alliances prior to entering the arena. You’ve dedicated your life to qualifying for the Grand Festivus Games, and you have the skills (and the scars) to prove it.

### Scenes

:::{.panel-tabset}
#### 0. Tavern

This morning someone passed you a note promising information that will give you an edge in the arena. After some careful consideration, you have decided to meet the informant at a tavern on the other side of town. When you arrive at the tavern, you are ushered into a private room at the back.

Anyone caught trying to throw the games will be disqualified, so you are a little concerned when you recognize several other contestants at the table. A serving maid brings in drinks and dinner.

*give players time to mingle*

*Nox enters the room. He sits at the table and studies each individual in turn and frowns at the empty chair. After letting some dramatic tension build, he finally speaks.*

"Welcome, contestants. My employer has invited you all here this evening to provide some valuable information. The only thing I ask in return is that you make sure *<pick a player>* wins the Games. *<player who should win>*, you will be required to split your winnings with the others."

"Anyone who would like to forfeit your reward and maintain plausible deniability may leave now - if word of this meeting leaks out, I will find you and the consequences will be unpleasant."

*pause*

"Excellent."

*Nox describes the challenges they will face and distributes a copy of the map for Round 1.*

"Do you have any questions?"

*Answer questions - make up answers. Here are a few sample questions with answers.*

* What is in it for your employer?
  * The employer will be placing a wager on the winner.
* Why did you pick us?
  * We have been following all the contestants. You aren't exactly favored to win on your own, but together you have a high chance of winning. This will give us a bigger return on our bet.

"Very well, each of you place your hand on this orb before you leave."

*Individuals take turns placing a hand on the orb. When they do, a cold feeling passes over them, like a bucket of ice water was dumped over their heads. The feeling passes as quickly as it came.*

#### 1. Arena

*Round opens in the arena. There is a dense fog that has decreased visibility to less than 5 feet in any direction. The DM places players on a private map, including the direction they are facing. Players will need to wander blindly until they run into enough features on the map to pinpoint their location and then make their way to the tower.*

*Pair up each player with a non-player character from the list of contestants below.*

Each of you have been paired with another contestant. Either you both continue to the next round or neither of you does. You have one hour to make it to the tower, so don't dawdle. Anyone left in the arena is disqualified when the time expires.

##### Each turn

* Player specifies which direction to travel (relative to the direction they are facing) and how far they want to travel.
* If they are not running and there are no hostile creatures in the area, roll d20 for treasure
  * Reveal treasure chest (might be a mimic). If they decide to open the chest:
    * First chest they find contains weapons.
    * Subsequent chests contain additional treasure.

```{r}
data.frame(Roll = c('1 - 8', '9 - 11', '12 - 14', '15 - 16', '17 - 18', '19 - 20'),
           Weapon = c('',
                      'Shortbow: +4 to hit, 1d6 + 2 piercing damage',
                      'Push dagger (2): +3 to hit, 1d6 + 2 piercing damage',
                      'Long sword: +3 to hit, 1d8 + 3 slashing damage',
                      'Battle Axe: +3 to hit, 1d8 + 3 slashing damage',
                      'Great sword: +3 to hit, 2d6 slashing damage'),
           Treasure = c('No chest found', 'Torch', '50 ft of Rope', 'Potion of healing (+2d8 HP)', 'Potion of strength (+2 strength for 3 turns)',  'Candy')) |>
  kable()
```

When they reach the castle, they climb to the top and ring a bell

##### Hazards

* Trench and Pit
  * Trench is 10 ft across and 15 feet deep. There is a steep, rocky slope at either end that can be scrambled up (or down) without too much difficulty.
  * Pit is 30 ft across.
  * Creatures falling into it make an acrobatics check to see if they can catch themselves on the side. Creatures running through the fog (i.e. not walking) have disadvantage on the check.
    * 15 = Grab side. The creature must use their next action to climb out of the pit or trench.
    * 10 = Land on ledge 8 ft down. Creatures on a ledge can attempt to climb out at the beginning of a turn with a DC 10 athletics check.
    * Fail: fall to the bottom (15 feet down) and take 1d4 damage. Creatures can attempt to climb out with the help of a companion (i.e. the contestant each player has been paired with). Both players must pass a DC 10 athletics check for success.

##### Disqualified
  * Grognac
  * Thrór Mountainhelm
  * Oskar Diamondvein
  * George
  * Breey
  * Stormwind
  * Goldhelm
  * Nox
  
#### 2. Tower

##### Central Chamber
*The round opens in the central chamber of the tower.*

The goal of this round is to find a golden heart and make back out of the tower before time is up. Alliances are encouraged at this stage. Any group exiting the tower together will be able to move on to the next round, as long as they have at least one golden heart in their possession. You have 25 minutes to complete the round.

##### Bridge over underground stream
The path you picked leads to a stairwell descending into a cavern and eventually to a bridge crossing an underground stream.

*The Shadowfell come onto the scene from the opposite direction. There is a confrontation and xxx casts a spell that collapses the bridge, dumping our heroes into waist deep water. Any attempt to regain the path is thwarted by the Shadowfell.*

*Our heroes see the Shadofell find a golden heart, and the last we hear from them is their laughter as the heroes wade down stream.*

##### Underground river
*A sufficient investigation check in this area or the next will reveal a golden heart hidden in the river. Some gems may also be prized from the walls in places?*

##### Another bridge is found
As you continue downstream, you hear voices arguing ahead. As you come around a bend in the river, you see another bridge high above. On the bridge are some other contestants. You can tell they are arguing, but it is unclear what they are arguing about.

*The Masters have found an exit but no golden heart. They are reasonable and will agree to pull you up out of the river in exchange for letting them join your group to exit the tower.*

##### Disqualified

* Eve
* Beni
* Windy
* Vindex
* Lux
* Grom

#### 3. Gobstacle Course

*Teams navigate a treacherous obstacle course filled with traps and hostile enemies. Use dexterity checks, athletics checks, and teamwork to overcome the obstacles.*

The goal of this round is to reach the castle gates within 25 minutes. Go!

Turn order:

* Troll
* Goblins
* Shadowfell
* Heroes
* Masters
* Dwarves

##### Turn 1
*As one, the Shadowfell charge across the bridge, leaving Elara at the foot of the bridge to slow down the rest of the contestants. As they near the center of the bridge, an enormous troll jumps out from under the bridge and demands payment from anyone who wishes to cross. The Shadowfell stop briefly, trying to decide what to do.*

##### Turn 2
*The Shadofell don't have any coin and decide to attack the troll. Flickerclaw gets thrown off the bridge.*

##### Turn 3
*Thunderstone turns into a ram and butts the troll off the bridge.*

##### Turn 4
*Turns continue*

##### Turn 5
*The troll spends a turn climbing back over the edge of the bridge.*

##### Each subsequent turn:

* Player specifies desired action (if dashing, they get 2x speed, but no option for treasure)
* Events
  * Goblin attack: 4 goblins are hiding in the Gobstacle Course. They attack and use their *Nimble Escape* bonus action to disengage and hide in a nearby location.
  * Troll attack (see above)
  * Engage another NPC
  * Bear trap: 1d4 damage and spend the rest of your turn disengaging the trap.
  * Pit trap: 1d4 damage and fall into the pit. Options for escape (one per turn, takes the entire turn):
    * Alone - DC 15 athletics check
    * A second character in the pit and willing to help  - DC 10 athletics check
    * Someone outside of the pit and willing to help - DC 10 athletics check
    * Someone outside of the pit with a rope - DC 5 athletics check
  * Else - Roll d20 for treasure (unless they are running or being chased)

```{r}
data.frame(Roll = c('1 - 8', '9 - 10', '12 - 14', '15 - 16', '17 - 18', '19 - 20'),
           Treasure = c('No chest found', '50 ft of Rope', 'Potion of healing (+2d8 HP)', 'Potion of strength (+2 strength for 3 turns)', 'Potion of spider climbing (duration: one scene)', 'Candy')) |>
  kable()
```

##### Disqualified

Try to keep the following NPCs in play into Scene 4. If they don't make it, improvise. Use your judgement to decide when to make the cutoff for disqualification.

* Cinderheart
* Thunderstone
* Vidar
* Maya
* Falkenheim Flintbeard

#### 4. Dragon

*Contestants gather outside of the gate to a small courtyard. A tower can be seen rising from the other side of the compound. The door in the gate opens and a tall humanoid with silver hair steps out to greet you.*

Welcome contestants! You have shown yourselves to be both brave and clever. This last challenge will require both bravery and wit. Only one of you can win - the first to reach the top of the tower.

*The strange man beacons them to enter, and as they file into the courtyard but before the contestants have a chance to do anything, the creature with silver hair transforms into a hulking, ancient silver dragon, who stands between them and victory. On the opposite side of the courtyard is an archway with stairs ascending up into the tower.*

*Everyone stares in awe at the great beast. Falkenheim looses two bolts at the dragon, one bounces harmlessly off his chest and the other goes up the dragon's nose. The dragon roars, grabs Falkenheim in his mouth, bites a few times - his armor can be heard crunching and screeching on the dragon's teeth. Then the dragon throws the hapless dwarf over the courtyard wall.*

*The remaining Shadowfell immediately charge the dragon, with Cinderheart attempting to sneak around and up the stairs as Thunderstone does her best to distract the dragon - other NPCs may or may not join. Players must decide to watch or join the rush without discussing with each other.*

* Optional outcomes, depending on which of the players decide to join the rush.
  * The dragon uses his fearsome gaze to frighten all characters in the rush and they run out the gate and out of sight. Allow players to pass the required charisma check (unless they fail too badly). Any who pass the charisma check run across the courtyard and are caught by the dragon’s tail. They slam into the wall and drop to the ground in a daze, taking damage.
  * The dragon releases his breath weapon, paralyzing everyone in the courtyard. Any players rushing the dragon and passing the required constitution check are caught by the dragon’s tail. They slam into the wall and drop to the ground in a daze.

Dragon: "Oh, dear, no. That will not do at all. You must pass a test before you will be allowed to ascend to the top of the tower. Answer my riddles, and you will be rewarded."

*The dragon recites the first riddle, closes his eyes and settles in, waiting patiently for the correct answer. Further attempts to sneak by are met with stronger responses. Allow players time to discuss the potential answer.*

*At some point Vidar gets excited and whispers to Maya. After a brief exchange, Vidar charges the dragon. As he nears, Vidar feints to the right and dashes to the left, dodging a tail swipe. While he does this, Maya drinks a potion of spider climbing and attempts to run up the outside of the tower. The dragon swats her out off the wall before she makes it very far, and she lands in a heap in the courtyard. Vidar dodges one more tail swipe and manages to reach the stairs just ahead of the clawed hand of the dragon.*

*Dragon recites the second riddle. Give players a few more minutes to discuss.*

*After a few minutes Vidar can be seen peeking around the side of the arched entryway. He is hesitant to come out, but the dragon notices him and invites him back out. He sheepishly joins the rest of the contestants and reports that the stairs lead to a dead end.*

*Dragon recites the third riddle.*

##### Riddles

> My scales shimmer silver, my wings unfurl like vast plains,
> I hold the key to the treasure promised by these games.
> Atop a tower of stone, a hero may claim their due,
> But victory rests closer, within reach, if you know what to do.


> Two paths diverge, both reaching the sky,
> One built of stone, the other alive and high.
> One holds wind and treasure beyond compare,
> The other, a journey that will lead nowhere.
> Choose wisely, mortals, for time is fleeting,
> Only one path holds the prize you're seeking.


> I am the bridge between earth and sky,
> A soaring promise, a whispered reply.
> The tower reaches, a finger of stone,
> But true ascent comes when you're not alone.
> Seek not the highest point, but the truest guide,
> For only on wings of silver can wisdom confide.

##### Conclusion

*When a player asks for a ride to the top of the tower, the dragon smiles and says:*

Well done, heroes!

*The winning player uses the spikes along the dragon’s foreleg to climb to a spot just above his wings. The dragon then flies the player on a victory lap around the arena and deposits them on the top of the tower. They are rewarded with riches beyond their imagination.*

:::

### Creatures

:::{.panel-tabset}

#### Heroes

Here are some sample characters you can use if players don't bring their own.

* Gearshift - Gnome Rogue
  * HP: 21
  * AC: 14
  * Speed: 25 ft
  * Actions
    * Cunning Action: You can take a bonus action on each of your turns to take the Dash, Disengage, or Hide action.
    * Sneak Attack: Once per turn, you can deal an extra 2d6 damage to one creature you hit with an attack with a finesse or ranged weapon if you have advantage on the attack roll. You don't need advantage on the attack roll if another enemy of the target is within 5 ft. of it, that enemy isn't incapacitated, and you don't have disadvantage on the attack roll.
* Aenwyn - Elf Monk
  * HP: 21
  * AC: 14
  * Speed: 45 ft
  * Actions:
    * Unarmed strike: +5 to hit, You can punch, kick, head-butt, or use a similar forceful blow and deal 1d4 + 3 bludgeoning damage. When you use the Attack action with an unarmed strike or a monk weapon on your turn, you can make one unarmed strike as a bonus action.
    * Mask of the Wild: You can attempt to hide even when you are only lightly obscured by foliage, heavy rain, falling snow, mist, and other natural phenomena.
  * Bonus actions: You can spend Ki Points to fuel ki features. You have 3 points per round.
    * Flurry of blows: After you take the Attack action on your turn, you can spend 1 ki point to make two unarmed strikes as a bonus action.
Whenever you hit with one of your Flurry of Blows attacks, you can impose one of the following effects on that target: fall prone if it fails a DEX saving throw (DC 11), get pushed up to 15 ft. if it fails a STR saving throw (DC 11), or it can't take reaction until the end of your next turn.
    * Patient defense: You can spend 1 ki point to take the Dodge action as a bonus action on your turn.
    * Step of the wind: You can spend 1 ki point to take the Disengage or Dash action as a bonus action on your turn, and your jump distance is doubled for the turn.
  * Reactions:
    * Deflect missiles: You can use your reaction to deflect or catch the missile when you are hit by a ranged weapon attack. When you do so, the damage you take from the attack is reduced by 1d10 +6. If you reduce damage to 0 and have a free hand, you can spend 1 ki point to make a ranged attack (as with a monk weapon) with a range of 20/60. (+5 to hit, 1d4 + 3 damage)
    * Opportunity Attack: You can make an opportunity attack when a hostile creature that you can see moves out of your reach. To make the opportunity attack, you use your reaction to make one melee attack against the provoking creature. The attack occurs right before the creature leaves your reach
* Morok - Half-orc Fighter
  * HP: 30
  * AC: 14
  * Speed: 30 ft
  * Actions
    * Unarmed strike: You can punch, kick, head-butt, or use a similar forceful blow. +4 to hit, 3 bludgeoning damage
    * Second Wind: Once per scene, you can use a bonus action to regain 1d10 + 3 HP.
    * Action Surge: You can push yourself beyond your normal limits for a moment. Once per scene, you can take one additional action on your turn.
  * Reactions
    * Opportunity Attack: You can make an opportunity attack when a hostile creature that you can see moves out of your reach. To make the opportunity attack, you use your reaction to make one melee attack against the provoking creature. The attack occurs right before the creature leaves your reach
* Corvus, Dragonborn Paladin
  * HP: 25
  * AC: 16
  * Speed: 30 ft
  * Actions
    * Unarmed Strike: +5 to hit, 4 bludgeoning damage
    * Breath Weapon (gold): Once per round you can use your action to exhale a blast of fire. Each creature in a 15 ft line must make a DC 11 dexterity saving throw. On a failed saving throw they take 2d6 fire damage or half as much on a failed save.
    * Channel divinity: Once per round you may choose to channel divine energy to fuel magical effects for your action. When you use your Channel Divinity, you choose which option to use.
    * Sacred weapon: As an action you can imbue a weapon with positive energy. For six turns, the weapon is considered magical, you add +2 to attack rolls, it emits bright light for 20 ft. and dim light for 20 ft beyond that.
    * Turn the unholy: As an action, you can censure fiends and undead (e.g. zombies). Each fiend or undead that can see or hear you within 30 ft. must make a WIS saving throw (DC 12). On failure, it is turned for 1 minute or until it takes damage. A turned creature must spend its turns trying to move as far away from you as it can, and it can’t willingly move to a space within 30 feet of you. It also can’t take reactions. For its action, it can use only the Dash action or try to escape from an effect that prevents it from moving. If there’s nowhere to move, the creature can use the Dodge action.
    * Lay on Hands: You have a pool of healing power that can restore a total of 15 HP during the game. As an action, you can touch a creature to restore any number of HP remaining in the pool, or 5 HP to either cure a disease or neutralize a poison affecting the creature.
    * Spells: You may cast a total of three spells during the game.
      * Command: You speak a one-word command to a creature you can see within range. The target must succeed on a Wisdom saving throw (DC 12) or follow the command on its next turn. The spell has no effect if the target is undead, if it doesn't understand your language, or if your command is directly harmful to it.
      * Cure wounds: A creature you touch regains 1d8 + 2 hit points.
Protection from evil and good: Until the spell ends, one willing creature you touch is protected against certain types of creatures: aberrations, celestials, elementals, fey, fiends, and undead.
      * The protection grants several benefits. Creatures of those types have disadvantage on attack rolls against the target. The target also can't be charmed, frightened, or possessed by them. If the target is already charmed, frightened, or possessed by such a creature, the target has advantage on any new saving throw against the relevant effect.
      * Sanctuary: You ward a creature within range against attack. For the next six turns, any creature who targets the warded creature with an attack or a harmful spell must first make a DC 12 Wisdom saving throw. On a failed save, the creature must choose a new target or lose the attack or spell. This spell doesn't protect the warded creature from area effects, such as the explosion of a fireball.
      * Shield of faith: A shimmering field appears and surrounds a creature of your choice within range, granting it a +2 bonus to AC for the round.

#### Contestants

##### Dwarves

Strongly aligned and working together.

* Falkenheim Flintbeard - prince of Stonekeep of Falkenheim. Use [Dwarf Veteran](https://johnsonra.github.io/bestiary/creature/dwarf-veteran) stats. Survives into Scene 4.
* Baragor Stonehammer: [Druid](https://johnsonra.github.io/bestiary/creature/druid). Survives into Scene 3.
* Thrór Mountainhelm: Cleric. Use [ixitxachitl-cleric](https://johnsonra.github.io/bestiary/creature/ixitxachitl-cleric) stats, but replace *Bite* action with a short sword (same stats), and ignore the *Barbed tail* reaction. Thrór is eliminated during Scene 1.
* Oskar Diamondvein: Ranger. Use [Dwarf Veteran](https://johnsonra.github.io/bestiary/creature/dwarf-scout) stats. Oskar is eliminated during Scene 1.
* Rigel Cragfist: Wizard. Use [Dwarf mage](https://johnsonra.github.io/bestiary/creature/dwarf-mage) stats. Survives into Scene 3.
  
##### Shadowfell

Strongly aligned - have joined forces to win. Not so good guys. Cheating - if you end up dead along the way, they are OK with that. Cinderheart is planning to win and take the whole prize. Everyone else is expecting a cut of the winnings.

* Cinderheart - Tiefling rogue, leader of the group. Use [Tiefling Brawny Rogue](https://scottrpg.com/dnd/book-of-npcs-2.0/Tiefling/Level-03-Tiefling-NPCs.html#TieflingBrawnyRogue3) stats.
* Flickerclaw - Kobold Sorcerer. Use [Kobold Dragon Sorcerer](https://scottrpg.com/dnd/book-of-npcs-2.0/Kobold/Level-03-Kobold-NPCs.html#KoboldDragonSorcerer3) stats. Survives into Scene 3.
* Elara - Elven Monk. Use [Elf Earth Warden](https://scottrpg.com/dnd/book-of-npcs-2.0/Elf/Level-03-Elf-NPCs.html#ElfEarthWarden3) stats. Survives into Scene 3.
* Grognac - Orc Barbarian. Use [Orc](https://johnsonra.github.io/bestiary/creature/orc) stats. Eliminated during Scene 1.
* Thunderstone - Dwarf Druid. Use [Druid](https://johnsonra.github.io/bestiary/creature/druid) stats. Survives into Scene 3.

##### Masters
Not strongly aligned. These characters meet during Scenes 1 and 2, and they work together throughout the campaign

* Vidar - Survives into Scene 4.
  * Short sword: +3 to hit, 1d6 + 2 piercing damage
  * Hook and chain: +3 to hit, 1d4 piercing. When you throw this weapon, you can use your bonus action to pull it back into your hand. Additionally, when you hit a creature with this weapon via a thrown attack, you can use a bonus action to force a contested Strength (Athletics) check against the target. On a success, you can pull the target anywhere in range, as long as it is towards you.
* Kireri - Survives into Scene 3.
  * Spear: +3 to hit, 2d6 piercing damage
* Maya - Survives into Scene 3.
  * Battle Axe: +3 to hit, 1d8 + 3 slashing damage
damage
* Aethel - Survives into Scene 3.
  * Battle Axe: +3 to hit, 1d8 + 3 slashing damage

##### Other contestants

Eliminated during Scene 1:

  * George
  * Breey
  * Stormwind
  * Goldhelm
  * Nox
  
Eliminated during Scene 2:

  * Eve
  * Beni
  * Windy
  * Vindex
  * Lux
  * Grom
    
#### Named NPCs

* Nox - Shady character whose employer is trying to throw the games for gain.
* Lumenumbra - Ancient Silver Dragon encountered in Scene 4.
  * AC: 22
  * HP: 487
  * Speed: 40 ft, 80 ft when flying
  * Actions
    * Multiattack: The dragon can use its Frightful Presence. It then makes three attacks: one with its bite and two with its claws.
      * Bite. Melee Weapon Attack: +17 to hit, reach 15 ft., one target. Hit: 21 (2d10 + 10) piercing damage.
      * Claw. Melee Weapon Attack: +17 to hit, reach 10 ft., one target. Hit: 17 (2d6 + 10) slashing damage.
      * Tail. Melee Weapon Attack: +17 to hit, reach 20 ft., one target. Hit: 19 (2d8 + 10) bludgeoning damage.
    * Frightful Presence: Each creature of the dragon’s choice that is within 120 feet of the dragon and aware of it must succeed on a DC 21 Wisdom saving throw or become frightened for 1 minute. A creature can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success. If a creature’s saving throw is successful or the effect ends for it, the creature is immune to the dragon’s Frightful Presence for the next 24 hours.
    * Breath Weapons (Recharge 5-6). The dragon uses one of the following breath weapons.
      * Cold Breath. The dragon exhales an icy blast in a 90-foot cone. Each creature in that area must make a DC 24 Constitution saving throw, taking 67 (15d8) cold damage on a failed save, or half as much damage on a successful one.
      * Paralyzing Breath. The dragon exhales paralyzing gas in a 90- foot cone. Each creature in that area must succeed on a DC 24 Constitution saving throw or be paralyzed for 1 minute. A creature can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success.
    * Change Shape. The dragon magically polymorphs into a humanoid or beast that has a challenge rating no higher than its own, or back into its true form. It reverts to its true form if it dies. Any equipment it is wearing or carrying is absorbed or borne by the new form (the dragon’s choice). In a new form, the dragon retains its alignment, hit points, Hit Dice, ability to speak, proficiencies, Legendary Resistance, lair actions, and Intelligence, Wisdom, and Charisma scores, as well as this action. Its statistics and capabilities are otherwise replaced by those of the new form, except any class features or legendary actions of that form.
  * Legendary Actions: The ancient silver dragon can take 3 legendary actions, choosing from the options below. Only one legendary action option can be used at a time, and only at the end of another creature’s turn. The ancient silver dragon regains spent legendary actions at the start of its turn.
    * Detect. The dragon makes a Wisdom (Perception) check.
    * Tail Attack. The dragon makes a tail attack.
    * Wing Attack (Costs 2 Actions). The dragon beats its wings. Each creature within 15 ft. of the dragon must succeed on a DC 25 Dexterity saving throw or take 17 (2d6 + 10) bludgeoning damage and be knocked prone. The dragon can then fly up to half its flying speed.
    
#### Creatures

##### Scene 1

* Black Guard Drake
  * HP: 52
  * AC: 14
  * Speed: 30ft
  * Attacks twice: 
    * Bite. Melee Weapon Attack: +5 to hit, reach 5 ft., one target. Hit: 7 (1d8+3) piercing damage.
    * Tail. Melee Weapon Attack: +5 to hit, reach 5 ft., one target. Hit: 6 (1d6+3) bludgeoning damage.
* Chest Mimic
  * HP: 58
  * AC: 12
  * Speed: 15 ft
  * Adhesive (Not really an attack). The mimic adheres to anything that touches it. A Huge or smaller creature adhered to the mimic is also grappled by it (escape DC 13). Ability checks made to escape this grapple have disadvantage.
  * Attacks:
    * Pseudopod. Melee Weapon Attack: +5 to hit, reach 5 ft., one target. Hit: 7 (1d8 + 3) bludgeoning damage. If the mimic is in object form, the target is subjected to its Adhesive trait.
    * Bite. Melee Weapon Attack: +5 to hit, reach 5 ft., one target. Hit: 7 (1d8 + 3) piercing damage plus 4 (1d8) acid damage.
* Giant Boar
  * HP: 42
  * AC: 12
  * Speed: 40 ft
  * Attacks:
    * Charge. If the boar moves at least 20 ft. straight toward a target and then hits it with a tusk attack on the same turn, the target takes an extra 7 (2d6) slashing damage. If the target is a creature, it must succeed on a DC 13 Strength saving throw or be knocked prone.
    * Tusk. Melee Weapon Attack: +5 to hit, reach 5 ft., one target. Hit: 10 (2d6 + 3) slashing damage.
* Swarm of Rats
  * HP: 24
  * AC: 10
  * Speed: 30 ft
  * Attacks:
    * Bites. Melee Weapon Attack: +2 to hit, reach 0 ft., one target in the swarm’s space. Hit: 7 (2d6) piercing damage, or 3 (1d6) piercing damage if the swarm has half of its hit points or fewer.
* Zombie Cow
  * HP: 15
  * AC: 10
  * Speed: 30 ft
  * Attacks
    * Gore. Melee Weapon Attack: +6 to hit, reach 5 ft., one target. Hit: 7 (1d6+4) piercing damage.

##### Scene 3

* Goblins
  * HP: 7
  * AC: 15
  * Speed: 30 ft
  * Nimble Escape: The goblin can take the Disengage or Hide action as a bonus action on each of its turns.
  * Attacks:
    * Scimitar. Melee Weapon Attack: +4 to hit, reach 5 ft., one target. Hit: 5 (1d6 + 2) slashing damage.
    * Shortbow. Ranged Weapon Attack: +4 to hit, range 80/320 ft., one target. Hit: 5 (1d6 + 2) piercing damage.
* Troll
  * HP: 84
  * AC: 15
  * Speed: 30 ft
  * Multiattack. The troll makes three attacks: one with its bite and two with its claws.
    * Bite. Melee Weapon Attack: +7 to hit, reach 5 ft., one target. Hit: 7 (1d6 + 4) piercing damage.
    * Claw. Melee Weapon Attack: +7 to hit, reach 5 ft., one target. Hit: 11 (2d6 + 4) slashing damage.
    
:::
